Typed Functional Genetic Programming

### 2013-06-21 tex/thesis.tex
v3 now running ok (but..)
V zásedě jediná podstatná zmena oproti v2 je předělání Eva monády (+
pročištění).
Z nějakýho důvodu to ale je asi míň efektivní než to předtim což se
projevuje
u BA pro pop 5000 to hodi stackoverflow co to předtim v pohodě zvladalo.
found the bug in algorithm design of polyIM, started work on new design with MGU
..
[tex] outline of GP..

\section{Genetic Programming}
	\subsection{Term generating}
	\subsection{Crossover}
	\subsection{Mutation}

@@

	\textbf{TODO} 
	\begin{itemize} 
		\item TALK ABOUT "parenthesis" conventions (and packing of lambda abstractions). 
	\end{itemize}

@@

\chapter{ Designed system }	
	\section{Top level view}
		\subsection{Comments about main source files}
			\subsubsection{ Eva.hs }
	\section{Term generating}
		\subsection{A* algorithm}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.

>>>>

\section{Genetic Programming}

	\textit{Genetic programming} (GP) is a technique inspired by biological evolution
	that for a given problem tries to find computer programs able to solve that problem.

	A problem to be solved is given to GP in a form of \textit{fitness function}. 
	Fitness function is a function which takes computer program as its input and 
	returns numerical value called \textit{fitness} as output. 
	The bigger fitness of a computer program is, the better solution of a problem it is.

	GP maintains a collection of computer programs called \textit{population}. 
	A member of population is called \textit{individual}. 
	By running GP algorithm evolution of those individuals is performed.

	\Lets describe GP algorithm briefly.

	At the beginning initial population is generated randomly.

	A step of GP algorithm is stochastic transformation of the current population into 	
	the next population.

	This step consists of two sub steps\footnote{TODO : Technically it is done in a little  
	bit different fashion which is equivalent.}:
	\begin{itemize} 
		\item Selection of \textit{parents} for individuals of the next population based on the   		          fitness.
		      The bigger fitness of an individual of the current population is, 
		      the better chance of success being selected as parent it has.  
		\item Application of genetic operators (such as \textit{crossover}, 
		      \textit{reproduction} and \textit{mutation}) 
			  on parent individuals producing new individuals of the next population.  
	\end{itemize}	  
	This transformation is repeatedly applied for a predefined number of steps (which is called 
	number of \textit{generations}) or until some predefined criterion is met.

	...
	\\\\
	\textbf{TODO}
	\begin{itemize} 
		\item TALK ABOUT GP is part of EA etc. and maybe define the GP by defining EA and then
		      specifying the differences or something like that...    
		\item History, citations, etc ....
	\end{itemize}

	\subsection{Input}
	\subsection{Output}
	\subsection{GP algorithm}
		\subsubsection{Generating initial population}
		\subsubsection{Selection}
		\subsubsection{Crossover}
		\subsubsection{Reproduction}
		\subsubsection{Mutation}

@@

	\textbf{TODO} 
	\begin{itemize} 
		\item TALK ABOUT "parenthesis" conventions (and packing of lambda abstractions).
		\item BETTER SPECIFICATION $V$ is infinite spočetná (?countable)
	\end{itemize}

@@

\chapter{ Designed system }	
	\section{Top level view}
		\subsection{Comments about main source files}
			\subsubsection{ Eva.hs }
			\subsubsection{ GP\_{}Core.hs }
	\section{Term generating}
		\subsection{A* algorithm}
	\section{Crossover}
		\subsection{Finding same types}
		\subsection{Two basic options}
		Resolve problems with free variables or avoid variables completely.
